\chapter{Appendices for Chapter \ref{ch:Komar2013}}
\label{app:Komar2013}

\section{Derivation of reflected mode operator}
\label{App: Reflection}

We obtain the reflected mode operator $c_R$ using input-output
relations for a two-sided cavity. 
By assuming that the two endmirrors have
the same transmittivity ($\propto\kappa$), we can write the input-output
relation for cavity mode $c_a$ on the driven mirror as
\bel
	c_{a,\text{out}} =
	\sqrt{\kappa}c_a - c_{a,\text{in}},
\eel
where $c_{a,\text{in}} = -i\frac{\Omega}{\sqrt{\kappa}}$ is the incoming field
operator on the mirror and $c_{a,\text{out}}$ is the output field operator.
For direct comparision with $c_a$ we
divide by $\sqrt{\kappa}$ and define the
reflection mode operator as  
$c_R \equiv c_{a,\text{out}}/\sqrt{\kappa} =
c_a +i\frac{\Omega}{\kappa}$.


\section{Analytic model}
\label{sect:App:steady_state}


%\label{sec:analytic_model}


In this appendix we provide the analytic solutions
used to calculate one- and two-time
correlation functions in steady state.
First, one-time correlations are calculated
from  the steady state solutions of
Eqs.~(\ref{eq:c000}--\ref{eq:c022}).
We set the time derivatives to zero and
solve the equations iteratively,
order by order in the weak drive.
This procedure yields
\bal
	\label{eq:alpha000}\bar A_{000} &\approx& 1,\\
	\label{eq:alpha100}\bar A_{100} &=& -i\alpha \frac{1}{1 + 4x^2},\\
	\label{eq:alpha011}\bar A_{011} &=& -\alpha \frac{2x}{1 + 4x^2},\\
	\label{eq:alpha200}\bar A_{200} &=& -\frac{\alpha^2}{\sqrt{2}}\frac{1 + 2x^2}{(1 +
	4x^2)(1 + 6x^2)},\\
	\label{eq:alpha111}\bar A_{111} &=& i\alpha^2\frac{2x}{(1 + 4x^2)(1 + 6x^2)},\\
	\label{eq:alpha022}\bar A_{022} &=& \alpha^2\frac{4x^2}{(1 + 4x^2)(1 + 6x^2)},
\eal
where $\alpha = \Omega/\tilde\kappa$ ($|\alpha|^2 \ll 1$), $x = g/(4\tilde\kappa)$ and
$\tilde \kappa = \kappa -i\Delta$.  
Using these amplitudes, we can express all
equal time averages.
The mean photon numbers are
\bal
	\bar n_a &=& |\bar A_{100}|^2 ,\\
	\bar n_s &=& |\bar A_{011}|^2 ,\\
	\bar n_R &=& \left|\bar A_{100} + i\frac{\Omega}{\kappa}\right|^2,
\eal 
and the photon-photon correlation functions are
\bal
\label{eq:g2aa0}
	g^{(2)}_{aa}(0) &=& \frac{2|\bar A_{200}|^2}{|\bar A_{100}|^4},\\
\label{eq:g2ss0}
	g^{(2)}_{ss}(0) &= & \frac{2|\bar A_{022}|^2}{|\bar A_{011}|^4},\\
\label{eq:g2AA0}
	g^{(2)}_{RR}(0) &= &
	\frac{\left|-\left(\frac{\Omega}{\kappa}\right)^2+
	2i\frac{\Omega}{\kappa}\bar A_{100} +
	\sqrt{2}\bar A_{200}\right|^2}
	{\left|i\frac{\Omega}{\kappa}+\bar A_{100}\right|^4}.
\eal
To
leading order in $\kappa/g$ these
yield Eqs.~(\ref{eq:na}--\ref{eq:g2AA}).


At finite temperature we calculate steady state amplitudes
within each phonon subspace $n$ similarly
in the ansatz of \refeq{eq:psi_thermal}.
Using the  notation $R_\kappa(\omega)$ introduced 
in Section \ref{sec:onetime_correlation},
the steady state amplitudes
within the subspace with $n$ phonons in the optical
groundstate are
\begin{align}
%p_{1,0,n}=
|\bar A_{10n}|^2=&\frac{\Omega^2\sqrt{R_\kappa(0)}}
{R_{\kappa}\left(\frac{g}{2}\sqrt{n+1}\right)},\\
|\bar A_{01n+1}|^2=&\frac{\Omega^2 g^2 (n+1) }{4
R_{\kappa}\left(\frac{g}{2}\sqrt{n+1}\right)},\\
|\bar A_{20n}|^2 =&\frac{ \Omega^4
R_\kappa(g/\sqrt{8})}{R_\kappa\left(g\sqrt{(2n+1)/8}\right)R_\kappa\left(\frac{g}{2}
\sqrt{n+1}\right)},\\
|\bar A_{02n+2}|^2 =&\frac{ \Omega^4 g^4 (n+1) (n+2)}{32
R_\kappa\left(g\sqrt{(2n+1)/8}\right)R_\kappa\left(\frac{g}{2}
\sqrt{n+1}\right)}.
\end{align}


Two-time correlation functions are calculated similarly,
using the conditional state after a jump
(see Eqs.~(\ref{eq:psi^a}) and (\ref{eq:psi^s}))
as the initial condition.
For example the
unnormalized state after detection of a photon in the
$c_a$ mode is $c_a\ket{\psi} =  \bar A_{100}\ket{000} +
	\sqrt{2}\bar A_{200}\ket{100} + \bar A_{111}\ket{011}$. 
We solve
Eqs.~(\ref{eq:c000}--\ref{eq:c011}) for the amplitudes 
with this state as initial
condition.
The finite delay correlation of the driven mode is
\bel
\begin{split}
	&g^{(2)}_{aa}(\tau) = \frac{|A_{100}(\tau)|^2}{|\bar A_{100}|^4}.
\end{split}
\eel
in good agreement with the numerics.
The correlation of the undriven
mode $g^{(2)}_{ss}(\tau)$ is calculated similarly. 
The unnormalized
state after detection in the $c_s$ mode is  $c_s\ket{\psi} = 
\bar A_{011}\ket{001}  + \bar A_{111}\ket{101} +  \sqrt{2}
\bar A_{022}\ket{012}$.
Using this  as the
initial
condition we solve Eqs.~(\ref{eq:c001}--\ref{eq:c012}) for the amplitudes
in the conditional state. 
In the limit of $\gamma \ll \kappa$ we obtain
\bel
	g^{(2)}_{ss}(\tau) 
	=
	\frac{|A_{012}(\tau)|^2}{|\bar A_{011}|^4}.
\eel 

