\chapter{Introduction and Motivation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Overview and Structure}
The field of quantum science aims to answer conceptual and practical questions
about the fundamental behavior, controllability and applicability of 
systems governed by quantum physics. Such systems arise whenever a few 
degrees of freedom of a physical system become isolated from their environment. 

Realizing and maintaining the required isolation is a formidable
task. The interaction within the isolated components needs to be
much stronger than the collective coupling to modes of the environment.
Once achieved, the system starts to explore an expanded set of states: Its
dynamics are not constrained to a countable number of pointer (or
``classical'') states anymore, originally selected by the environment, rather it
moves around smoothly in the entire Hilbert space, with its motion governed by a
Hamilton operator. Internal components of such a system are said to be ``strongly
coupled'', and their dynamics to be ``coherent''.

The variety of (``quantum'') states in the Hilbert space  gives rise
to counter-intuitive phenomena such as superposition, tunneling and
entanglement.
Besides being academically exciting, these phenomena hold the promise that
future devices and protocols relying on them will perform better than any
conceivable scheme based solely on classical dynamics. 

The discovery of
efficient quantum algorithms for problems that are conjectured to not be
efficiently computable fueled the field of Quantum Computing. In Chapters
\ref{ch:Komar2013} and \ref{ch:Stannigel2012}, we analyze the
capabilities of nano-scale optomechanical systems to perform coherent logical
operations, the elemental steps of quantum computation.

Protocols that rely on entanglement to distribute secret keys between distant
parties are the main focus of Quantum Communication. Their security is based on
fundamental physical limitations, rather than practical one due to
computational complexity.
In Chapters \ref{ch:Borregaard_PRL2015} and \ref{ch:Borregaard_PRA2015}, we
describe how a system consisting of a few atoms isolated in an optical cavity
can be used to realize a quantum gate with integrated error detection, and we
analyze its usefulness in a quantum communication setup.

The idea of preparing a detector in a quantum
superposition in order to focus its sensitivity to the quantity of interest is
the central topic of Quantum Metrology. In Chapters \ref{ch:Kessler2014},
\ref{ch:Komar2014} and \ref{ch:Komar2015}, we present a
protocol for operating a network of atomic clocks, which combines local and
remote entanglement to surpass the accuracy of classical protocols and
asymptotically reach the fundamental quantum limit of precision, the Heisenberg limit. 


 
 
 
 
 
 
\section{Optomechanical Systems}
The current fabrication technology allows the creation of integrated devices
with nanometer-scale features such as waveguides \cite{Mekis1996}, photonic
band-gap materials \cite{Foresi1997}, non-linear inductive elements
\cite{Makhlin1999}, antenna arrays \cite{Yu2014}, optical cavities
\cite{Painter2001}, and mechanical resonators of various shapes and sizes
\cite{Aspelmeyer2014}.

Coupling components with different physical properties can give rise to devices
which incorporate the best characteristics of each component.
Optical components are fast ($\sim 100-1000\,\mathrm{THz}$) and fairly isolated,
however, making them strongly interact with each other is challenging
\cite{Chang2007}.
Mechanical components, on the other hand, are much slower ($\sim
0.01-10\,\mathrm{GHz}$), but are usually much more sensitive to changes in their
surroundings \cite{Aspelmeyer2014}. One successful application is using
mechanical elements as transducers between two optical degrees of freedom allows
for efficient filtering and frequency conversion \cite{Eichenfield2009} when
driven by classical light.

The interaction between the light field and a mechanical surface originates
mainly from the light-pressure displacing the mechanics, and gives rise to a
non-linear parametric coupling between light intensity and mechanical motion
\cite{Meystre2013}. In Chapter \ref{ch:Komar2013}, we analyze a quantum model of
two optical cavities and a mechanical oscillator interacting through this
coupling. We find that if the system is driven by a weak laser pulse (accurately
described by a Poisson-process of photon arrivals), the output light exhibits
super- and sub-Poissonian characteristics. We find that if the system is
properly tuned, and is sufficiently cooled down, then it can be used for
coherent quantum operations.
If the energy difference between the two optical modes is bridged by the
mechanical mode, then we can use the photons leaving the output port to herald
the creation of a single mechanical excitation.

Using oscillators as quantum registers in a future quantum computer requires
them to be anharmonic \cite{Majer2007}. This is because consecutive levels of an
anharmonic oscillator are separated by unequal frequency intervals, which makes
it possible to address transitions independently. The inherent
non-linearity of the optomechanical coupling holds the promise of rendering the
coupled oscillator system sufficiently anharmonic for computational tasks. In
Chapter \ref{ch:Stannigel2012}, we propose a quantum logic architecture based on
coupled optomechanical components. We find that, under sufficiently strong
cooling, the system exhibits non-classical behavior and is able to store
information and perform logic gates on the qubits.






\section{Atom-Cavity Systems}
Coupling individual atoms to optical cavities is one of the most effective ways
to realize a well-controllable and manifestly quantum system \cite{Mabuchi2002,
Walther2006}.
The first model, named after E. Jaynes and F. Cummings \cite{Jaynes1963,
Shore1993}, describes the coherent dynamics of a single transition between two
levels of an atom and a single, confined optical mode. This model is exactly
solvable and serves as a great source of intuition.

As the physical size of an optical cavity is decreased, the zero-point
electric field corresponding to the ground state of its modes increases.
As a result, individual atoms placed inside such a cavity, coupled through their
electric dipole moment, start to interact strongly with the optical modes. Once
this interaction becomes much stronger than the coupling of the atoms to the
radiation environment outside of the cavity, the system becomes strongly coupled, and
their states hybridize. From a spectroscopic point of view, this results in a
resolvable splitting of the optical resonances.

Optical cavities built on photonic crystal waveguides \cite{Tiecke} have
high zero-point electric fields, and produce couplings
to atoms larger than their spontaneous emission rate. Their
observed lifetime is then considerably decreased \cite{Englund2005}; an effect
called Purcell-enhancement.

Once such strong interaction is demonstrated, the prospect of using these
systems for coherent quantum logic operations becomes realistic. In Chapter
\ref{ch:Borregaard_PRL2015}, we consider a model of three atoms placed inside
and coupled by a single optical cavity. We show that with tailored driving pulses
and a proper choice of atomic levels this system can perform a controlled-NOT
operation on two of the atoms and can be made tolerant to the dominating error,
caused by the loss of a photon, by post-selecting on the state of the third
atom.

\section{Quantum Repeaters}
Creating quantum entanglement between systems separated by
large distances is the most important prerequisite of quantum communication
protocols. Experimental realizations rely on exchanging weak light pulses
via carefully monitored optical fibers \cite{Peev2009}. The
reliability of direct transmission of photon pulses is limited by the
fiber attenuation length, the maximum of which ($\sim 20\,\mathrm{km}$) is
achieved at telecom wavelength ($\sim 1\,\mu\mathrm{m}$).

Classical communication solves the attenuation problem by incorporating fiber
segments which amplify the signal. Conceptually, this classical amplification
relies on detecting some of the signal photons and emitting more in synchrony.
Unfortunately, such a process fails for quantum channels using single-photon
pulses, because the detection event can measure the photon only once,
therefore it necessarily discards essential information about its quantum state.

Overcoming the attenuation problem in quantum channels requires using more
resources. The scheme of quantum repeaters consists of repeater stations placed
between the sender and the receiver \cite{bennett2, bennett, duan3}.
These stations, instead of relaying the information forward, create pairwise
entanglement with their neighbors using direct photon transmission via 
fibers, which are much shorter than the total length. Once all entangled pairs
are heralded, each station performs a local quantum logic operation between the
two pairs that they have access to. This is called entanglement connection,
resulting in entanglement between the two outermost parties. An alternative solution 
encodes the information in states of a many-photon pulse, and applies periodic
quantum error-correction along its way \cite{Muralidharan2015}.

The transmission rate  and reliability of such a quantum repeater protocol
depends strongly on the fidelity of the entanglement connection step. In Chapter
\ref{ch:Borregaard_PRA2015}, we show that the atom-cavity system described
in Chapter \ref{ch:Borregaard_PRL2015} would serve as a great quantum
entanglement connection gate, and achieve outstanding quantum repeater
performance for total distances of $\sim 100-1000\,\mathrm{km}$.



\section{Atomic Clocks and Quantum Metrology}
Currently, atomic clocks are the best time-keeping devices. They are
used to create and broadcast a precise time and
frequency standard. The workings of atomic clocks rely on two main components: the
reference oscillator, realized by an isolated, narrow-linewidth electromagnetic
transition of an atomic species, \cite{Derevianko2011} and the slaved
oscillator, the microwave or optical source of a strong, coherent field. The
clock keeps time by periodically interrogating the atoms with the field of the
slaved oscillator (laser), and measuring the deviation of their frequencies.
The measurement result is then used to correct the frequency of the laser.
This closes the feedback loop, and results in an actively stabilized laser
field, which serves as the clock signal \cite{Diddams2004}.

The accuracy of an atomic clock, characterized by the average fractional
frequency deviation, the Allan-deviation \cite{Allan1966, Rutman1978}, is
determined by several factors. Employing higher atomic reference frequency,
longer interrogation cycles, longer averaging time and more atoms improve
the overall accuracy. Consequently, there are many independent ways to improve
the accuracy:
Choosing an atomic transition with optical frequency, instead of microwave,
boosts the performance of the clock by five orders of magnitude. The central
frequencies of the current record-holder atomic clocks are all in the optical
domain \cite{Ludlow2015}. The optimal length of the interrogation cycle usually falls
slightly above the coherence time of the laser, and in any case, increasing it
fails to help beyond the atomic coherence time even in schemes that eliminate
the limiting effect of the laser \cite{Borregaard2013, Rosenband2013}. The
maximal total averaging time is usually determined by the refresh rate of the
clock signal required by the application, or by other noises such as frequency
flicker noise \cite{Barnes1966}.

The dependence of the precision on the number of atoms is a true quantum
phenomenon.
It is due to the fundamental limit on the maximal information a single
measurement can obtain about the atoms. When $N$ atoms are measured
independently, the Allen-deviation scales as $\propto N^{-1/2}$, and is limited
by projection noise. This limit is called the ``Standard Quantum Limit''. It
originates from the inherent uncertainty of a single two-level system prepared in superposition \cite{Santarelli1998}.
 
The Standard Quantum Limit describes the limit of precision if all atoms are
prepared and measured independently, or as an uncorrelated ensemble. Although it
is accurate in most cases, it is higher than the fundamental quantum limit, due
to Heisenberg uncertainty. The latter predicts $\propto N^{-1}$ scaling of the
precision with atom number $N$ \cite{Hall2012}. The gap between the
two limits, and proposals trying to close it, is the main focus of
Quantum Metrology \cite{Giovanetti2011, Escher:2011fn}.

By preparing the collection of atoms in an
entangled state, the subsequent measurement will have lower uncertainty and will
provide more information about the detuning of the laser frequency from the
atomic reference. States such as squeezed states \cite{Andre2004,
Borregaard2013_nearHeisenberg}, Greenberger-Horne-Zeilinger (GHZ) states
\cite{Wineland1998, Bollinger1996}, and optimally entangled states
\cite{Buzek1999, Berry2009}, all promise a significant improvement, and some
even reach the Heisenberg limit for large $N$. In Chapter \ref{ch:Kessler2014},
we calculate a limit on the best achievable performance using a cascade of GHZ
states, and compare it with the other algorithms. We find that for total
averaging times shorter than the atomic coherence time, the precision of our
scheme surpasses the precision of the best classical protocol.

Once we establish that entangling the available atoms is beneficial, finding the
optimal protocol for a network of atomic clocks becomes an important problem. In
Chapter \ref{ch:Komar2014}, we assume that a large number of identical atomic
clocks are joined together in a quantum network using a quantum communication
scheme. We show that this network can be operated in a way that every clock
atom is entangled with all atoms in the network, forming a global, multi-party
GHZ state. We characterize the enhancement of the overall precision and compare
it with precisions of schemes using only local or no entanglement.





\section{Rydberg Blockade}
In most cases, interactions between atoms in cold ensembles are accurately
modeled by short-range or contact interactions \cite{Cheng2010}.
They can be neglected if the gas is not too dense, and the duration of the
phenomena under investigation is short compared to the inverse of average
collision rate. This breaks down when a few atoms acquire significant magnetic
or electric dipole moments and, as a result, start interacting via dipole-dipole
interaction, whose strength scales as $\propto R^{-3}$ with separation $R$.

One way to induce a strong electric dipole moment in an atom is to optically
excite the outermost electron to a level with high principle quantum number ($n
> 30$), a Rydberg level. Rydberg levels have small energy spacing
($\propto n^{-3}$), long spontaneous lifetimes ($\propto n^3$), and strong
transition dipole moments ($\propto n^2$) \cite{Saffman2010}. These properties
make Rydberg atoms a promising tool to realize fast and reliable quantum
logic operations \cite{Lukin2001}.  

Blockade between Rydberg atoms is an especially strong and promising phenomenon.
When one atom gets excited into a Rydberg state, the long-range interaction
originating from its (transition) electric dipole moment shifts the Rydberg
levels of all other atoms out of resonance, and prevents them from being excited
\cite{Urban2009}. This effect creates an exceptionally strong non-linearity: it
limits the number of Rydberg excitations in the cloud to zero and one, allowing
the cloud to be used as a qubit. In Chapter \ref{ch:Komar2015}, we present and
analyze a quantum protocol that relies on strong Rydberg blockade to perform
fast, high-fidelity operations between different quantum registers. We propose
to use different delocalized spin-waves of the atomic cloud to store
information, and employing the Rydberg blockade to mediate interactions between
them. We show that even after taking the physical imperfections into account,
our scheme provides a feasible way to prepare the network-wide global GHZ state
required by the quantum clock network of Chapter \ref{ch:Komar2014}.

 









