%% frontmatter.tex
%%

\title{Quantum Information Science and Quantum Metrology: Novel Systems and
Applications}
\author{P\'{e}ter K\'{o}m\'{a}r}
\degreemonth{December} % month final submission occurs.
\degreeyear{2015}
\degree{Doctor of Philosophy}
\field{Physics} 
\department{Physics}
\advisor{Mikhail D. Lukin} % Category I added.

\maketitle
\copyrightpage
  

\begin{abstract} 
% limited to 1.5 pages, double-spaced (Registrar's Office guidelines).
% Also limited to 350 words. I claim $\mu \sim \omega^4$ is a single word.

The current frontier of our understanding of the physical universe is dominated
by quantum phenomena. Uncovering the prospects and limitations of acquiring and
processing information using quantum effects is an outstanding challenge in
physical science. This thesis presents the analysis of several new model systems
and applications for quantum information processing and metrology.

First, we analyze quantum optomechanical systems exhibiting quantum phenomena in
both optical and mechanical degrees of freedom. We investigate the strength of
non-classical correlations in a model system of two optical and one mechanical
mode.  We propose and analyze experimental protocols that exploit these
correlations for quantum computation.

We then turn our attention to atom-cavity systems involving strong coupling of
atoms with optical photons, and investigate the possibility of using them as
robust information storage and relay nodes.
We present a scheme for a robust two-qubit quantum gate with inherent
error-detection capabilities. We consider several remote
entanglement protocols employing this robust gate, and we use this system to
study the performance of the gate in practical applications.

Finally, we present a new protocol for running multiple, remote atomic clocks in
quantum unison. We show that by creating a cascade of independent GHZ states 
distributed across the network, the scheme asymptotically reaches the
Heisenberg limit, the fundamental limit of measurement accuracy. We propose an
experimental realization of such a network consisting of neutral atom clocks, 
and analyze the practical performance of such a system.




\end{abstract}



\newpage
\addcontentsline{toc}{section}{Table of Contents}
\tableofcontents

% these are optional in the Jan 2000 Harvard thesis GSAS guide:
\listoffigures
% use \caption[lst-entry]{Text of table caption} to define the title of the
% figure
\listoftables


% cccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccccc
\begin{citations}

\vspace{0.8in}

\ssp
\noindent
Most of the chapters of this thesis have appeared in print elsewhere. By
chapter number, they are:
\begin{itemize}
  	\item 
		Chapter \ref{ch:Komar2013}: 
		``Single-photon nonlinearities in two-mode optomechanics,'' 
		P. K\'{o}m\'{a}r,
		S. D. Bennett, 
		K. Stannigel,  
		S. J. M. Habraken,  
		P. Rabl,  
		P. Zoller, 
		and 
		M. D. Lukin, 
		\emph{Phys.	Rev.  A} 
		\textbf{87}, 
		013839 
		(2013).
  	\item 
		Chapter \ref{ch:Stannigel2012}: 
		``Optomechanical Quantum Information Processing with Photons and Phonons,'' 
		K. Stannigel,  
		P. K\'{o}m\'{a}r, 
		S. J. M. Habraken,  
		S. D. Bennett,
		M. D. Lukin,
		P. Zoller,   
		and P. Rabl, 
		\emph{Phys. Rev. Lett.} 
		\textbf{109},
		013603 (2012).
  	\item 
		Chapter \ref{ch:Borregaard_PRL2015}: 
		``Heralded Quantum Gates with Integrated Error Detection in Optical
		Cavities,'' 
		J. Borregaard, 
		P. K\'{o}m\'{a}r, 
		E. M. Kessler, 
		A. S. S{\o}rensen, 
		and M. D. Lukin,
 		\emph{Phys. Rev. Lett.} 
		\textbf{114},
		110502 (2015).
  	\item 
		Chapter \ref{ch:Borregaard_PRA2015}: 
		``Long-distance entanglement distribution using individual atoms in optical
		cavities,'' 
		J. Borregaard, 
		P. K\'{o}m\'{a}r, 
		E. M. Kessler, 
		A. S. S{\o}rensen, 
		and M. D. Lukin, 
 		\emph{Phys. Rev. A} 
		\textbf{92},
		012307 (2015).
  	\item 
		Chapter \ref{ch:Kessler2014}: 
		``Heisenberg-Limited Atom Clocks Based on Entangled Qubits,''
		E. M. Kessler, 
		P. K\'{o}m\'{a}r,  
		M. Bishof, 
		L. Jiang, 
		A. S. S{\o}rensen, 
		J. Ye, 
		and M. D. Lukin,
 		\emph{Phys. Rev. Lett.} 
		\textbf{112},
		190403 (2014).
  	\item 
		Chapter \ref{ch:Komar2014}: 
		``A quantum network of clocks,''
		P. K\'{o}m\'{a}r,  
		E. M. Kessler, 
		M. Bishof, 
		L. Jiang, 
		A. S. S{\o}rensen, 
		J. Ye, 
		and M. D. Lukin,
 		\emph{Nature Physics} 
		\textbf{10},
		582–587 (2014).
	\item 
		Chapter \ref{ch:Komar2015}: 
		``Quantum network of netural atom clocks,''
		P. K\'{o}m\'{a}r,  
		T. Topcu, 
		E. M. Kessler, 
		A. Derevianko, 
		J. Ye,
		V. Vuleti\v{c},
		and M. D. Lukin,
 		\emph{arXiv:} 
 		\warn{\ldots},
		(2015).			 
\end{itemize}

\end{citations}




\begin{acknowledgments}

First of all, I would like to thank my research advisor, Prof. Mikhail Lukin,
for his scientific insights and ideas, and especially for his attention and
patience in guiding my work and education.

I would like to thank other members of my thesis committee, Prof. John Doyle
and Prof. Subir Sachdev, with whom I was fortunate to work
 as a teaching fellow. Their knowledge and thoroughness
inspired both my teaching and research.

I am grateful to Prof. Andrei Derevianko at University of Nevada, Prof.
Pierre Meystre at University of Arizona, Prof. Peter Rabl in Vienna, Till
Rosenband at Harvard, Prof. Anders S{\o}rensen in Copenhagen, Prof. Vladan
Vuleti\v{c} at MIT, Prof. Jun Ye at JILA, and Prof. Peter Zoller in Innsbruck
for the enlightening discussions and their invaluable contributions to my
research in the past five years.

I would like to thank all colleagues with whom I worked namely, Michael Bishof,
Soonwon Choi, Manuel Endres, Ruffin Evans, Michael Goldman, Michael Gullans,
Steven Habraken, M\'{a}rton Kan\'{a}sz-Nagy, Shimon Kolkowitz, Ronen Kroeze,
Peter Maurer, Travis Nicholson, J\'{a}nos Perczel, Thibault Peyronel, Arthur
Safira, Alp Sipahigil, Kai Stannigel, Alex Sushkov, Jeff Thompson, Turker Topcu,
Dominik Wild, Norman Yao, Leo  Zhou. I am especially grateful to Steven Bennett,
Johannes Borregaard, and Eric Kessler; besides many years of fruitful
collaboration, they helped me as mentors and friends.

I would also like to thank David Morin, Jacob Barandes, Nick Schade and people
from the Bok Center, John Girash, Colleen Noonan, and Matthew Sussman, for
their efforts in guiding me to become a better teacher.

I am thankful for my friends in Cambridge and Boston: Travis and John Woolcott,
who gave me tremendous help during my first year, and continued to keep an eye
on me; Bence B\'{e}ky and Margit Szabari for teaching me the tricks and
traditions of living in the US; and Kartiek Agarwal, Debanjan Chowdhury and Ilya
Feige for our endless discussions about life.

The Physics Department staff has been an invaluable resource.
I would like to thank
Monika Bankowski, Jennifer Bastin, Lisa Cacciabaudo, Karl Coleman, Carol Davis,
Sheila Ferguson, Joan Hamilton, Dayle Maynard, Clare Ploucha, Janet Ragusa and
Sarah Roberts, for helping me at countless occasions.

I am grateful to the Harvard International Office, and especially to Darryl
Zeigler, for all the help making me feel myself at home at Harvard.

I am thankful to the Office of Career Services, and especially Laura Stark and
Heather Law, for helping me transition to the next stage of my career.

Finally, I would like to thank my family, Erzs\'{e}bet K\'{o}m\'{a}r, Antal
K\'{o}m\'{a}r, Anna K\'{o}m\'{a}r and Szilvia Kiriakov, for their immense
support and understanding towards my education and work. I cannot thank you
enough. This thesis is dedicated to you.
 






 




\end{acknowledgments}





%ddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddddd
\dedication

\begin{quote}
\hsp
\em
\raggedleft

Dedicated to my parents Erzs\'{e}bet and Antal,\\
my sister Anna,\\
and my fianc\'{e}e Szilvia.

\end{quote}


\newpage

\startarabicpagination

%%% end

